A``Periodic Table'' for Bravais Lattices

### 2024-11-25 DeloneGrid/DeloneGrid.tex
????

	\aff[a]{9515 NE 137th St, Kirkland, WA, 98034-1820 \country{USA}}
	\aff[b]{c/o NSLS-II, Brookhaven National Laboratory, Upton, NY, 11973 \country{USA}}

@@

	\citeasnoun{Delaunay1932} and \citeasnoun{Delone1975} published a table of the Bravais types
	as distinguished by Selling (Delaunay) reduction.\cite{andrews2023measuring} published
	a somewhat modified version of Delaunay's table. The table presented here
	is arranged with the lattice family types as columns and the Federov polyhedron
	types as rows.
			\begin{figure}
		\includegraphics[width=10cm]{HorizontalDeloneGrid}
		\label{grid}
		\caption{The  Bravais lattice types.}
	\end{figure}

@@

The International Tables for x-ray crystallography \cite{vonLaue1952}
used the convention of labeling Selling parameters in the Bravais
tetrahedron, as \textbf{P}, \textbf{Q}, \textbf{R}, \textbf{S}, \textbf{T}, \textbf{U}, corresponding to the \SVI{} scalars
\Svec, respectively. For reference,
the figure has been included in the upper left cell of the table.
		\begin{figure}
		\includegraphics[width=5cm]{PQRSTU}
		\label{PQRSTU}
		\caption{The key cell with the labels used in the
		International Tables}
	\end{figure}

@@

	At the right end of the table, a few examples of Dirichlet
	cells for each row.

	\cite{fedorov1885elements}

@@

	Prominent in the table are cells shown in gray. They have no
	corresponding Bravais type. For instance, the cell that would be
	$\bf{H1}$ would be a hexagonal cell with no zero parameters
	(this is no 90$^{\circ}$ angles); 
	clearly impossible.

@@

	Within the table there are five cells that have a yellow
	background. Although Delaunay identified these among the 24
	Bravais types, they are special in the sense that they
	do no possess the full dimensionality of their lattice
	family. Most likely, they are only of minor crystallographic 
	interest.

@@

	$\bf{O3}$ is a 2-D manifold that is the boundary between
	 $\bf{O2}$ and $\bf{O1B}$.
	With a characteristic of (rs0 rs0), $\bf{O3}$ has only two
	free parameters, not the three that is normal for an 
	orthorhombic unit cell.

>>>>

	\aff[a]{9515 NE 137th St, Kirkland, WA, 98034-1820 \country{USA}}
	\aff[b]{Fresh Pond Research Institute, c/o NSLS-II, Brookhaven National Laboratory, Upton, NY, 11973 \country{USA}}

@@

	\citeasnoun{Delaunay1932} and \citeasnoun{Delone1975} published a table of the Bravais types
	as distinguished by Selling (Delaunay) reduction.\cite{andrews2023measuring} published
	a somewhat modified version of Delaunay's table. The table presented here in Fig. \ref{grid}
	is arranged with the lattice family types as columns and the Federov polyhedron
	types \cite{fedorov1891symmetry} \cite{fedorov1885elements} as rows.
		\begin{figure}
		\includegraphics[width=15cm]{HorizontalDeloneGrid.eps}
		\label{grid}
		\caption{The  Bravais lattice types.}
	    \end{figure}

@@

The International Tables for x-ray crystallography \cite{vonLaue1952}
used the convention of labeling Selling parameters in the Bravais
tetrahedron, as \textbf{P}, \textbf{Q}, \textbf{R}, \textbf{S}, \textbf{T}, \textbf{U}, corresponding to the \SVI{} scalars
\Svec, respectively. For reference,
the figure has been included in the upper left cell of the table.  The values of the six
Selling parameters given in the PQRSTU order unabiguously identify the cell and is called
the ``\SVI{} characteristic'' of the cell type, given at the bottom center of each cell of
the table..  Note in particular which Selling
parameters are zero, denoting right angles among them, and which ones are equal,
denoting cases of higher symmetry.
	\begin{figure}
		\includegraphics[width=5cm]{PQRSTU}
		\label{PQRSTU}
		\caption{The key cell with the labels used in the
		International Tables}
	\end{figure}

@@

	At the right end of the table, there are a few examples of Dirichlet
	cells for each row.

@@

	The cells shown in gray have no corresponding Bravais type. For 
        instance, the cell that would be
	$\bf{H1}$ would be a hexagonal cell with no zero parameters
	(\it{i.e.} no 90$^{\circ}$ angles); 
	clearly an impossible case.

@@

	Within the table there are five cells that have a yellow
	background. Although Delaunay identified these among the 24
	Bravais types, they are special in the sense that they
	do not possess the full dimensionality of their lattice
	family. Most likely, they are of only minor crystallographic 
	interest.

@@

	$\bf{O3}$ is a 2-D manifold that is the boundary between
	 $\bf{O2}$ and $\bf{O1B}$.
	With a characteristic of (rs0 rs0), $\bf{O3}$ has only two
	free parameters, not the three that are normal for an 
	orthorhombic unit cell.
